Restructuring Spoken Corpus for Streaming Emulation

### 2020-04-25 2020-tsd-brno-restructuring/splits-anonymous.tex
add cicling2019 republication

\documentclass{llncs}
\usepackage{graphicx}

\begin{document}
\newtheorem{Definition}{Definition}
\title{Restructuring Spoken Corpus for Streaming Emulation}

\author{Jan Old\v{r}ich Kr\r{u}za}
%\author{Anonymous}

\institute{Charles University in Prague\\
           Faculty of Mathematics and Physics\\
           Institute of Formal and Applied Linguistics\\
           Malostransk\'{e} n\'{a}m\v{e}st\'{i} 25, Prague\\
           Czech Republic\\
           kruza@ufal.mff.cuni.cz}
%\institute{Anonymous university\\
%           Anonymous institute \\
%           Address\\
%           Country\\
%           E-mail}

\maketitle

@@

The algorithm sought seems to be a typical demonstration of dynamic programming:
Find an optimal split of a part of the recording that only consists of the first
word, then add next word and find the optimal split based on the current one.

There is also a simpler variant, however:
\begin{enumerate}
\item{start with the set of all
silences;}
\item{iterate over them from shortest to longest;}
\item{remove the silence
from the set if joining its adjacent segments doesn't yield one that's longer
than 60 seconds;}
\item{end iteration;}
\item{iterate again over chosen silences;}
\item{remove a silence from the
set if one of its adjacent segments is shorter than 30 seconds;}
\item{end iteration;}
\end{enumerate}

This algorithm is very easy to program and it has linear complexity.

@@

%
%\section*{Bibliography}
%    1. Reppen, Randi: Building a corpus: what are the key considerations?
%in collection The Routledge handbook of corpus linguistics, pages 59-65, 2010, Routledge
%    2. Crowdy: Spoken corpus design
%in journal Literary and Linguistic Computing 1993/4, pages 259-265, 1993, Oxford University Press
%    3. Hájek: Český mystik Karel Makoň
%in journal Dingir 2007/4, ISSN 1212-1371, pages 142-143, ed. Vojtíšek, 2007, Dingir s.r.o.
%    4. Ircing, Krbec, Hajič, Psutka, Khudanpur, Jelinek, Byrne: On large vocabulary continuous speech recognition of highly inflectional language-Czech
%in proceedings of Seventh European Conference on Speech Communication and Technology, 2001
%    5. Krůza, Peterek: Making Community and ASR Join Forces in Web Environment
%in proceedings of International Conference on Text, Speech and Dialogue, pages 415-421, 2012, Springer
%    6. Krůza, Kuboň: Second-Generation Web Interface to Correcting ASR Output
%in Proceedings of the Future Technologies Conference (FTC) 2018, ISBN 978-3-030-02685-1, ISSN 2194-5357, volume 1, pages 749-762, 2018, Springer
%    7. Psutka, Ircing, Psutka, Hajič, Byrne, Mírovský: Automatic transcription of Czech, Russian, and Slovak spontaneous speech in the MALACH project
%in proceedings of Ninth European Conference on Speech Communication and Technology, ISBN 1018-4074, pages 1349-1352, 2005, ISCA
%

\section*{Acknowledgments}

This work has been using language resources developed, stored and distributed by the LINDAT/CLARIN project of the Ministry of Education, Youth and Sports of the Czech Republic (project LM2010013).
\\
Participation in the conference was supported by COST action IS1404.
\\
This research was partially supported by SVV project number 260 104.

>>>>

% This is samplepaper.tex, a sample chapter demonstrating the
% LLNCS macro package for Springer Computer Science proceedings;
% Version 2.20 of 2017/10/04
%
\documentclass[runningheads]{llncs}
%
\usepackage{graphicx}
% Used for displaying a sample figure. If possible, figure files should
% be included in EPS format.
%
% If you use the hyperref package, please uncomment the following line
% to display URLs in blue roman font according to Springer's eBook style:
% \renewcommand\UrlFont{\color{blue}\rmfamily}

\begin{document}
%
\title{Restructuring Spoken Corpus for Streaming Emulation}
%
%\titlerunning{Abbreviated paper title}
% If the paper title is too long for the running head, you can set
% an abbreviated paper title here
%
\author{Anonymous Author\inst{1}}
%
% First names are abbreviated in the running head.
% If there are more than two authors, 'et al.' is used.
%
\institute{Anonymous Institute,\\
Anonymous University,\\
Adress Undisclosed\\
\email{anonymous@example.org}}
%
\maketitle              % typeset the header of the contribution
%

@@

The silences are selected by starting with the complete set and removing
shortest first while constraints remain kept.

@@

### 2020-04-25 2020-tsd-brno-restructuring/splits.tex
add cicling2019 republication

\begin{document}
%
\title{Restructuring Spoken Corpus for Streaming Emulation}
%
%\titlerunning{Abbreviated paper title}
% If the paper title is too long for the running head, you can set
% an abbreviated paper title here
%
\author{Anonymous Author\inst{1}}
%
% First names are abbreviated in the running head.
% If there are more than two authors, 'et al.' is used.
%
\institute{Anonymous Institute,\\
Anonymous University,\\
Adress Undisclosed\\
\email{anonymous@example.org}}
%
\maketitle              % typeset the header of the contribution
%

@@

>>>>

\begin{document}
%
\title{Restructuring Spoken Corpus for Streaming Emulation}
%
%\titlerunning{Abbreviated paper title}
% If the paper title is too long for the running head, you can set
% an abbreviated paper title here
%
\author{Jan Oldřich Krůza\inst{1}\orcidID{0000-0002-7510-6470}}
%
\authorrunning{Jan Krůza}
% First names are abbreviated in the running head.
% If there are more than two authors, 'et al.' is used.
%
\institute{Institute of Formal and Applied Linguistics,\\
Faculty of Mathematics and Physics,\\
Charles University\\
\email{kruza@ufal.mff.cuni.cz}}
%
\maketitle              % typeset the header of the contribution
%

@@

\section*{Acknowledgments}

This work has been using language resources developed, stored and distributed by
the LINDAT/CLARIAH project of the Ministry of Education, Youth and Sports of the
Czech Republic (project LM2018101).
